Passion Driven Statistics Project
========================================================


IF INTERNETUSERATE < 0 THEN INTERNETSCORE = .;
ELSE IF INTERNETUSERATE < 7.5 THEN INTERNETSCORE = 0;
ELSE IF INTERNETUSERATE < 20 THEN INTERNETSCORE = 1;
ELSE IF INTERNETUSERATE < 40.6 THEN INTERNETSCORE = 2;
ELSE IF INTERNETUSERATE < 65.2 THEN INTERNETSCORE = 3;
ELSE IF INTERNETUSERATE < 100 THEN INTERNETSCORE = 4;




/* To see the association of POLICYSCORE and  INTERNETSCORE */
IF POLITYSCORE = . THEN POLITYSCORE2 = .;
ELSE IF POLITYSCORE <= -5 THEN POLITYSCORE2=0;
ELSE IF POLITYSCORE <= 0 THEN POLITYSCORE2=1;
ELSE IF POLITYSCORE <= 5 THEN POLITYSCORE2=2;
ELSE POLITYSCORE2=3;

```{r}
data<-load("./gapminder_pds.RData")
#Data munging
gapminder_pds[is.na(gapminder_pds["polityscore"]),"polityscore2"]<-NA
gapminder_pds[(!is.na(gapminder_pds["polityscore"])  & gapminder_pds["polityscore"]<=-5),"polityscore2"] <- 0
gapminder_pds[(!is.na(gapminder_pds["polityscore"])  & gapminder_pds["polityscore"]>-5 & gapminder_pds["polityscore"]<=0),"polityscore2"] <- 1
gapminder_pds[(!is.na(gapminder_pds["polityscore"])  & gapminder_pds["polityscore"]>0 & gapminder_pds["polityscore"]<=5),"polityscore2"] <- 2
gapminder_pds[(!is.na(gapminder_pds["polityscore"]) & gapminder_pds["polityscore"]>5),"polityscore2"] <- 3


gapminder_pds[is.na(gapminder_pds["internetuserate"]),"internetscore"]<-NA
gapminder_pds[(!is.na(gapminder_pds["internetuserate"])  & gapminder_pds["internetuserate"]<=7.5),"internetscore"] <- 0
gapminder_pds[(!is.na(gapminder_pds["internetuserate"])  & gapminder_pds["internetuserate"]>7.5 & gapminder_pds["internetuserate"]<=20),"internetscore"] <- 1
gapminder_pds[(!is.na(gapminder_pds["internetuserate"])  & gapminder_pds["internetuserate"]>20 & gapminder_pds["internetuserate"]<=40.6),"internetscore"] <- 2
gapminder_pds[(!is.na(gapminder_pds["internetuserate"])  & gapminder_pds["internetuserate"]>40.6 & gapminder_pds["internetuserate"]<=65.2),"internetscore"] <- 3
gapminder_pds[(!is.na(gapminder_pds["internetuserate"])  & gapminder_pds["internetuserate"]>65.2),"internetscore"] <- 4

```


```{r fig.width=7, fig.height=6}



```

